Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-21 paper-filmat.tex
typo

The topos~$\Sh_{\neg\neg}(\E)$ is related to the \emph{double negation
translation}~$\varphi \mapsto \varphi^{\neg\neg}$ from classical logic into
intuitionistic logic: A statement~$\varphi$ holds in~$\Sh_{\neg\neg}(\E)$ if
and only if~$\varphi^{\neg\neg}$ holds
in~$\E$~\cite[Theorem~6.31]{blechschmidt:phd}.
% FUTURE: ultrapowers, gluing
\end{enumerate}

>>>>

The topos~$\Sh_{\neg\neg}(\E)$ is related to the \emph{double negation
translation} from classical logic into
intuitionistic logic: A statement holds in~$\Sh_{\neg\neg}(\E)$ if
and only if its translation holds
in~$\E$~\cite[Theorem~6.31]{blechschmidt:phd}.
% FUTURE: ultrapowers, gluing
\end{enumerate}
